\subsubsection{Fall 2018}
        \textbf{Week 4}
        \begin{itemize}
            \item We finished our problem statement this Thursday during class time (it was a lecture on research writing, which we are not doing), we then met with our TA and talked a bit about how those meetings would go and about the requirements document. We also did some research on the hardware we would need, we are planning on doing some basic testing with a raspberry pi and a camera module. We also met with our sponsor on Thursday where we asked questions about info we needed for the requirements document and also talked about some stretch goals.Our sponsor brought up some things he thought would be problems for us, primarily connecting our devices to the internet on location. This is another thing we will be looking in to when we start testing our equipment.
        \end{itemize}
         \textbf{Week 5}
        \begin{itemize}
            \item As a group we made a lot of progress on our system requirements document, we met with our sponsor and our TA (separately) and discussed what we had in our draft. We found out that we are missing some content that our sponsor wants us to have, as well as the Gantt chart. We will be meeting online this weekend to finish up our requirements document.We also had our sponsor request some hardware for us so that we can start testing.
        \end{itemize}
        \newpage
        \textbf{Week 6}
        \begin{itemize}
            \item In the past week, we finished up our requirements document draft, and I submitted my tech review draft earlier today. We also picked up a raspberry pi and camera module from Kevin so we can start testing stuff now. When giving us the device Kevin brought up the issue that Raspberry Pis struggle when streaming video so that may be a potential problem. We plan on meeting Tuesday after class to make a paper prototype for our sponsor, and we will also meet on Thursday to work on setting up the device. Over the weekend I plan on playing around with the Raspberry Pi and seeing what I can do.
        \end{itemize}
        \textbf{Week 7}
        \begin{itemize}
            \item Since last week I have finished my tech review and submitted it. As a group we also made a paper prototype for our sponsor. We haven't encountered any problems this week. I plan on making a lightweight interactive prototype over the weekend that we will be able to show our sponsor next week. In addition, now that we have a raspberry pi, camera module, and SD card we will be able to start testing the video capabilities of the Pi, testing the Pi may not start this week because of other coursework, but we have the option.
        \end{itemize}
        \textbf{Week 8}
        \begin{itemize}
            \item This past week I made a lightweight prototype for our sponsor and did some basic work setting up the raspberry pi. We ran in to an issue as a group trying to get the pi connected to the internet on campus but we figured it out now. We plan on getting drivers and using a monitor to work on the pi in the future.
        \end{itemize}
        \textbf{Week 9}
        \begin{itemize}
            \item Our group didn't do much in the past week. I did some testing with the raspberry pi and the first video streaming method I tried was too low quality for our project, I found another method using VLC but haven't gotten around to testing it yet.
        \end{itemize}
        
    \subsubsection{Winter 2018}
        \textbf{Week 1}
        \begin{itemize}
            \item Progress: Over the break my group set up some of the web pages that we will need to run our project. We currently have our login page as well as a basic main viewing page for both viewers and admins.

            \item Problems: No problems have come up yet.

            \item Plans: We found a meeting time that works for us, we just need to organize with our client to see if it works for him as well.
        \end{itemize}
        \textbf{Week 2}
        \begin{itemize}
            \item Progress: Added changing map functionality on the website, started setting up MySQL for site.

            \item Problems: Having issues connecting to the MySQL server with php, I'm using the code snippet provided by onid and it isn't working.

            \item Plans: Do elevator pitch and poster on Tuesday, message the IT dept about my issue.
        \end{itemize}
        \newpage
        \textbf{Week 3}
        \begin{itemize}
            \item Progress: We made our elevator pitch and poster draft, I did some work on getting SQL set up with the website but ran in to issues.

            \item Problems: Waiting for IT dept to resolve issue with connecting to MySQL server

            \item Plans: If the IT dept doesn't resolve my issue I will switch to a different method for connecting. Also planning on going in to their office physically next week.
        \end{itemize}
        \textbf{Week 4}
        \begin{itemize}
            \item Progress: Got the database set up and updated the map changing to use the database.

            \item Problems: None.

            \item Plans: Add/remove devices showing up on the map as well as a basic video page. Not actually displaying video or connecting to the devices as they aren't set up yet, just placeholder stuff.
        \end{itemize}
        \textbf{Week 5}
        \begin{itemize}
            \item Progress: Got the grid correctly displaying over the image, we also got the raspberry pi to stream video to another computer on the same network.

            \item Problems: None.

            \item Plans: We are meeting today to work on the progress update as well as streaming. Personally I am also working on the ability to add devices to be displayed on the map.
        \end{itemize}
        \textbf{Week 6}
        \begin{itemize}
            \item Progress: Devices can be added, moved, and removed from the map. Also started working on a dummy video page.

            \item Problems: We had some issues with connecting to the Raspberry Pi from an external network, also stream quality is pretty low so we might need to get the newer Pi.

            \item Plans: Get the newer version of the Pi, get on the robotics network at OSU so we can work on campus, finish up the stream page. We are also going to schedule a user study with one of my co-workers.
        \end{itemize}
        \textbf{Week 7}
        \begin{itemize}
            \item Progress: We did a usability test of our current website. I forget if this was in the last weeks update, but the website is fully functional, it just needs to be hooked up to the devices and made prettier. We also finished the progress update to turn on the for the class and will be reviewing it before turning it in.

            \item Problems: Nothing new.

            \item Plans: Make the website prettier, work on cross network streaming.
        \end{itemize}
        \textbf{Week 8}
        \begin{itemize}
            \item Progress: Made the website prettier, included the requested picture for the index page. We also just got cross network streaming working today.
            \item Problems: None.
            \item Plans: Get the video to stream to the website.
        \end{itemize}
        \newpage
        \textbf{Week 9}
        \begin{itemize}
            \item Progress: Changed the format we were outputting our stream in to make it easier to display on web It now streams when using safari but not chrome or firefox.
            \item Problems: It doesn't stream on chrome or firefox (yet, I've found a js library to help with that).
            \item Plans: Make the progress update video and get it streaming for other browsers.
        \end{itemize}
        \textbf{Week 10}
        \begin{itemize}
            \item Progress: Normal video streaming works on all browsers, made script and slides for our progress update.
            \item Problems: None on my end.
            \item Plans: Record the update video and work on 360 streaming.
        \end{itemize}
    
    \subsubsection{Spring 2019}
        \textbf{Week 1}
        \begin{itemize}
            \item Progress: Updated website to support multiple devices streaming and I think to support the 360 video (have yet to test), started working on some more style changes to meet client color requests. We got audio streaming to work, but have yet to merge it with the video.
            \item Problems: We had a couple of issues getting the audio to stream but we figured it out eventually.
            \item Plans: Merge audio with the video, test to see if 360 video works.
        \end{itemize}
        \textbf{Week 2}
        \begin{itemize}
            \item Progress: We have audio streaming to a file, currently working on getting it to the server
            \item Problems: So far the server is creating the file, but not writing to it.
            \item Plans: Meeting over the weekend to get the video and audio merged, get the 360 video working with that format, and writing install scripts and stuff in prep for code freeze
        \end{itemize}
        \textbf{Week 3}
        \begin{itemize}
            \item Progress: Got video and audio streaming, just got aframe to recognize our stream but it isn't formatted nicely yet

            \item Problems: No blockers, just need to do some tweaking for aframe

            \item Plans: Turn in our document revisions, make the 360 stream look better
        \end{itemize}
        \textbf{Week 4}
        \begin{itemize}
            \item Progress: Got 360 video working on our website, currently looks the same as normal video page but is 360. We also finished the poster for expo.

            \item Problems: None

            \item Plans: File down the 360 mirror to fit better on the camera. Do the matrix projection so that the 360 video is centered properly for aframe.
        \end{itemize}
        \textbf{Week 5}
        \begin{itemize}
            \item Progress: Finished poster, looked in to unwrapping video for aframe

            \item Problems: Currently unable to get the 360 to display properly in aframe, aframe does not seem to support native video transformation.

            \item Plans: Figure out how to reformat the 360 video.
        \end{itemize}
        \textbf{Week 6}
        \begin{itemize}
            \item Progress: got dewarping for 360, can turn it back in to video for a-frame

            \item Problems: rpi isn't strong enough to run it all at the same time

            \item Plans: strip down the dewarping script to the bare minimum, if it still isn't fast enough rewrite it in C and put it in our video recording program.
        \end{itemize}
        