\subsubsection{Fall 2018}
\textbf{Week 4}
\begin{itemize}
    \item Progress: We completed our problem statement, and met with our client again today. We met with our team TA. We also began working on the requirements document as well as posting everything to the GitHub page.
    \item Problems: We currently have not faced any problems at this point in our project.
    \item Plans: We plan to meet again on Thursday as a team, with our TA, and with our sponsor. We will also work more on our requirements document after we learn more about it during lecture, and with the TA office hours on Friday. 
\end{itemize}
\textbf{Week 5}
\begin{itemize}
    \item Progress: we have completed most of the requirements document and have also begun discussing the tech review. We will be having our TA review the requirements document before we submit it.
    \item Problems: After having our client review our requirements document, we discovered we needed to make some changes including the format and information presented. Our team will be meeting virtually on Saturday to complete the assignment.
    \item Plans: we will be completing the requirements document Saturday and sending it to our TA for a final review. We will then begin working on the tech review.
\end{itemize}
\textbf{Week 6}
\begin{itemize}
    \item Progress: We completed our requirements document, and delegated what we needed to research for the tech review.
    \item Problems: No problems this week, we are hoping to begin working on hardware developments soon.
    \item Plans: We are planning on completing a paper prototype next week, and then begin working on the design document.
\end{itemize}
\textbf{Week 7}
\begin{itemize}
    \item Progress: we completed the paper prototype and uploaded it into github so the sponsor can view it.
    \item Problems: No problems this week.
    \item Plans: We will begin the lightweight prototype and begin working with the raspberry pi to test streaming capabilities. We will also begin discussing the design document.
\end{itemize}
\textbf{Week 8}
\begin{itemize}
    \item Progress: we created the lightweight prototype and began working with the raspberry pie.
    \item Problems: no current problems to report.
    \item Plans: we will work more with the raspberry pie to take videos.
\end{itemize}
\newpage
\textbf{Week 9}
\begin{itemize}
    \item Progress: Due to the holiday we did not meet this week.
    \item Problems: we are experiencing some problems with streaming quality on the raspberry pie and further testing will be needed.
    \item Plans: we are working on the design document over break so we can finish it on Monday. 
\end{itemize}

\subsubsection{Winter 2018}
\textbf{Week 1}
\begin{itemize}
    \item Progress: we completed most of the website over winter break.
    \item Problems: no problems to report
    \item Plans: we are working on scheduling our TA and client meeting times for this term.
\end{itemize}
\textbf{Week 2}
\begin{itemize}
    \item Progress: we scheduled our meetings with our client and TA and discussed what we each are responsible for doing these next few weeks
    \item problems: due to some confusion we were unable to meet our TA this week but we resolved the confusion and will be meeting with them next week.
    \item Plans: we will be working more on finishing the final parts of the website and beginning working on hardware.
\end{itemize}
\textbf{Week 3}
\begin{itemize}
    \item Progress: met with our TA and our client, we also completed out poster draft and elevator speeches.
    \item Problems: some difficulty with the mySQL for the website but that is being resolved.
    \item Plans: we will continue to work on the hardware testing as well as the website.
\end{itemize}
\textbf{Week 4}
\begin{itemize}
    \item Progress: Began implementation of the A-frame network into our website.
    \item Problems: no problems this week.
    \item Plans: We have the poster critique session on Tuesday where we will improve upon our poster.
\end{itemize}
\textbf{Week 5}
\begin{itemize}
    \item Progress: we were able to stream the video to another computer on the same network.
    \item Problems: we are not able to stream the video to a computer on a different network.
    \item Plans: we will solve how to stream the video to a different network and order the other parts we need for the project.
\end{itemize}
\textbf{Week 6}
\begin{itemize}
    \item Progress: completed most of the website functionality and found someone to complete our use case test, and also put in a request for more hardware for out project.
    \item Problems: We are still not able to stream to another network.
    \item Plans: We will be working to get the raspberry pi to stream to another network, and will be possibly experimenting with using the robotics network.
\end{itemize}
\textbf{Week 7}
\begin{itemize}
    \item Progress: we completed a use case test on our website with a student where English is not their first language.
    \item Problems: no problems this week.
    \item Plans: Have the pi stream to different networks.
\end{itemize}
\textbf{Week 8}
\begin{itemize}
    \item Progress: obtained more hardware including a new raspberry pi.
    \item Problems: no new problems to report.
    \item Plans: we are meeting this Saturday to work on streaming to other networks.
\end{itemize}
\textbf{Week 9}
\begin{itemize}
    \item Progress: we were able to successfully stream the video to a different network.
    \item Problems: we are having difficulty streaming audio as we can only currently save audio instead of streaming it live.
    \item Plans: we will be solving the current problems of streaming audio as well as connecting the video stream to the website.
\end{itemize}
\textbf{Week 10}
\begin{itemize}
    \item Progress: obtained parts for the 360 degree camera.
    \item Problems: no problems this week.
    \item Plans: finish the final report for the term and complete the term video. Begin modeling the cases for our raspberry pi. 
\end{itemize}
\subsubsection{Spring 2019}
\textbf{Week 1}
\begin{itemize}
    \item Progress: I updated the website to add devices to include their IP address so we can actually stream from multiple devices.
    \item Problems: We were having some problems with streaming audio, but we might have a solution that we will be testing tonight.
    \item Plans: We will complete the audio streaming as well as streaming with the 360 video. We will also prepare everything for the code freeze on April 15th.
\end{itemize}
\textbf{Week 2}
\begin{itemize}
    \item Progress: we were able to stream audio across networks, and also improve the audio quality. 
    \item Problems: we had some problems with the sound quality and streaming.
    \item Plans: we will be completing everything for the code freeze.
\end{itemize}
\textbf{Week 3}
\begin{itemize}
    \item Progress: Completed the main part of our project for the code freeze.
    \item Problems: had trouble streaming the 360 video using A-frame.
    \item Plans: Fix the 360 stream and complete our final poster draft. 
\end{itemize}
\textbf{Week 4}
\begin{itemize}
    \item Progress: Completed our poster design to be reviewed and printed.
    \item Problems: No problems this week.
    \item Plans: 'dewrap' the 360 video so it can be seen properly in the stream. 
\end{itemize}
\textbf{Week 5}
\begin{itemize}
    \item Progress: We researched different solutions for 'de-wrapping' the 360 degree video.
    \item Problems: All of the current solutions that we have found will not work with our project since they do not work with live video streaming.
    \item Plans: Researching different ways we can manipulate the video using A-Frame. This way  the video can still be live and will be viewable in 360. 
\end{itemize}
\textbf{Week 6}
\begin{itemize}
    \item Progress: We got dewarping to work for pre-recorded 360 video.
    \item Problems : We do not have the processing power to run the dewarping live.
    \item Plans: Prepare everything we need for expo on May 17th . 
\end{itemize}